---
title: "Final Project"
author: "Trang Nguyen"
date: "2024-11-28"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tm)
library(tidyverse)
library(wordcloud)
library(readxl)
library(ggplot2)
library(nycflights13)
library(plotly)
library(DT)
library(stringr)
library(tinytex)
```





##Calories
The mean daily calorie intake is equal to or greater than 2000 calories
The mean daily calorie intake is less than 2000 calories
$H_0:\mu \ge 2000$ vs $H_0:\mu < 2000$

##Caffein
The mean daily caffeine intake is greater than or equal to 400 mg
The mean daily caffeine intake is less than 400 mg
$H_0:\mu \ge 400$ vs $H_0:\mu < 400$

##Sleep hour
The mean daily sleep duration is greater than or equal to 8 hours
The mean daily sleep duration is less than 8 hours
$H_0:\mu \ge 8$ vs $H_0:\mu < 8$


```{r}
Nguyen<-read_excel("~/Desktop/Fall 2024/Data 211 Data Science and Visualization/Final week /Nguyen data.xlsx")


## Calculate T test

cal_test <- t.test(Nguyen$`Total Calories`, mu = 2000, alternative = "less")
cal_test

caff_test <- t.test(Nguyen$`Caffein (mg)`, mu = 400, alternative = "less")
caff_test

sleep_test <- t.test(Nguyen$`Hour of sleep`, mu = 8, alternative = "less")
sleep_test



##ggplot between weight vs independent variable
ggplot(data=Nguyen, aes(x = `Total Calories`, y = `Weight (lbs)`)) +
  geom_point() +
  labs(
    title = "Weight vs Calories",
    x = "Food Calories",
    y = "Weight (lbs)")



ggplot(Nguyen, aes(x = `Hour of sleep`, y = `Weight (lbs)`)) +
  geom_point() +
  labs(
    title = "Weight vs. Hours of Sleep",
    x = "Hours of Sleep",
    y = "Weight (lbs)")

ggplot(Nguyen, aes(x = `Caffein (mg)`, y = `Weight (lbs)`)) +
  geom_point()+
  labs(
    title = "Weight vs. Caffeine Intake",
    x = "Caffeine (mg)",
    y = "Weight (lbs)")


##calculate mean
mean_calories <- mean(Nguyen$`Total Calories`, na.rm = TRUE)
mean_caffeine <- mean(Nguyen$`Caffein (mg)`, na.rm = TRUE)
mean_sleep <- mean(Nguyen$`Hour of sleep`, na.rm = TRUE)

thresholds <- c(2000, 400, 8)

summary_data <- data.frame(
  Metric = c("Calories", "Caffeine", "Sleep"),
  Mean = c(mean_calories, mean_caffeine, mean_sleep),
  Threshold = thresholds)

summary_data


ggplot(summary_data, aes(x = Metric)) +
  geom_bar(aes(y = Mean, fill = "Mean"), stat = "identity", position = "dodge") +
  geom_bar(aes(y = Threshold, fill = "Threshold"), stat = "identity", position = "dodge", alpha = 0.6) +
  labs(x = "Variable",y = "Values",fill = "Legend") 

```
Since the all $p$-value is less than $\alpha = 0.05$. Therefore, we reject the $H_0$. At a $5\%$ significance level. These results indicate that my intake and sleep habits are consistently below recommended levels.


